Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks in binary neural networks?

### 2021-12-09 docs/latex/manuscript.tex
Updates from Overleaf

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `manuscript')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[manuscript,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

%% These commands are for a PROCEEDINGS abstract or paper.

\def\@copyrightspace{\relax}
%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks?}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Tuan Pham}
\email{tuanph18@uchicago.edu}
\affiliation{%
  \institution{The University of Chicago}
  \city{Chicago}
  \state{Illinois}
  \country{USA}
}

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%% TO-DO
%%
%% The abstract is a short summary of the work to be presented in the
%% article.
%% TO-DO
\begin{abstract}
  \textbf{Insert ABSTRACT here}
\end{abstract}

@@

%% TO-DO
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig. \ref{fig:fig1}c). Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful. For now, we are unsure why. One of the reasons might be that we only allowed for 20 epochs per task for this benchmark while the original paper allowed for 40 epochs. Maybe larger networks require a bit more time to consolidate properly. We might run our training again with the exact same hyperparameter settings to see whether it might just have been some nuances in the settings.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.png}
    \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training. (a) Example of original (top, task 1) and generated permuted (bottom, after task 1) MNIST dataset. (b) Performance of the BNN (MLP, 2 hidden layers, 1024 units each) with different values of metaplasticity hyperparameter (c) Performance with variations in the number of hidden units per layer with meta = 1.35}
    \label{fig:fig1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.png}
    \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
    \label{fig:fig2}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.png}
    \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks. The model here is MLP BNN with 2 hidden layers of 2048 units each. See Fig \ref{fig:fig2}. for demonstrations of natural corruption. The x-axis for each panel represents where the original test data come from, e.g. task-2 in the shot\_noise panel means that the test dataset is the task-2 (permuted MNIST) that gets corrupted with shot\_noise corruption. }
    \label{fig:fig3}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.png}
    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. The test accuracy due to FGSM attacks is shown as a function of the perturbation strengths epsilons. Trained at task-01 refers to the end of the training phase in which the model was trained at MNIST dataset, while task-06 means that the model was the end of the entire metaplasticity training process. Only attacks on the original MNIST were tested here. Future iterations will integrate attacks on the following tasks (i.e. on pMNIST). }
    \label{fig:fig4}
\end{figure}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

@@

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

>>>>

\documentclass[manuscript,screen,review]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\def\@copyrightspace{\relax}

%%\citestyle{acmauthoryear}

\begin{document}

\title[Continual learning vesus robustness]{Do solutions for catastrophic forgetting degrade model robustness to naturalistic corruption and adversarial attacks in binary neural networks?}

\author{Tuan Pham}
\email{tuanph18@uchicago.edu}
\affiliation{%
  \institution{The University of Chicago}
  \city{Chicago}
  \state{Illinois}
  \country{USA}
}

@@

%% TO-DO
\begin{abstract}

\end{abstract}

@@

%% TO-DO: do we need this?
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

\keywords{neural networks, catastrophic forgetting, continual learning, robustness, natural corruptions, adversarial attacks}

\maketitle

@@

Additionally, we also try to replicate the relationship between the sizes of the hidden layers and the performance (Fig. \ref{fig1}c). Contrary to the monotonic trend between the trend and the performance shown in the original paper, we found that large networks could be harmful. For now, we are unsure why. One of the reasons might be that we only allowed for 20 epochs per task for this benchmark while the original paper allowed for 40 epochs. Maybe larger networks require a bit more time to consolidate properly. We might run our training again with the exact same hyperparameter settings to see whether it might just have been some nuances in the settings.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig1.pdf}
    \caption{Results of permuted MNIST tasks for the BNNs with metaplasticity training. (a) Example of original (top, task 1) and generated permuted (bottom, after task 1) MNIST dataset. (b) Performance of the BNN (MLP, 2 hidden layers, 1024 units each) with different values of metaplasticity hyperparameter (c) Performance with variations in the number of hidden units per layer with meta = 1.35}
    \label{fig:fig1}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig2.pdf}
    \caption{Examples of the natural corruptions for MNIST data, plotted with similar color limits}
    \label{fig:fig2}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig3.pdf}
    \caption{Test performance of the BNN models at the end of metaplasticity (colors) training in response to different monochrome natural corruptions (panels, original is last) generated from different tasks. The model here is MLP BNN with 2 hidden layers of 2048 units each. See Fig \ref{fig:fig2}. for demonstrations of natural corruption. The x-axis for each panel represents where the original test data come from, e.g. task-2 in the shot\_noise panel means that the test dataset is the task-2 (permuted MNIST) that gets corrupted with shot\_noise corruption. }
    \label{fig:fig3}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig4.pdf}
    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. The test accuracy due to FGSM attacks is shown as a function of the perturbation strengths epsilons. Trained at task-01 refers to the end of the training phase in which the model was trained at MNIST dataset, while task-06 means that the model was the end of the entire metaplasticity training process. Only attacks on the original MNIST were tested here. Future iterations will integrate attacks on the following tasks (i.e. on pMNIST). }
    \label{fig:fig4}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig5.pdf}
    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
    }
    \label{fig:fig5}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/report/Fig6.png}
    \caption{FGSM adversarial attack on MNIST data of the BNN trained with metaplasticity during permuted MNIST task for 2 different training phases of the model. 
    }
    \label{fig:fig6}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\appendix

@@

\end{document}
\endinput
